\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-07-29 write_up/mixfishsim_ecolmod.tex
Revisions in response to JJP and JMG

\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} appropriate
scales for spatial fisheries management has been a challenge in the past that
has led to ineffectual measures with unintended consequences. These unintended
consequences limited impacts towards management objectives, or increased
benthic impact on previously unexploited areas (e.g.  the cod closure in the
North Sea \citep{Rijnsdorp2001,Dinmore2003}). SENTENCE HERE ATTRIBUTING THE
CHALLENGE OF IDENTIFYING APPROPRIATE SCALES TO COURSE SPATIAL INFORMATION.
\replaced[id=PD]{M}{Since then
	m}ore refined spatial information has \added[id=PD]{since} become
available through the combination of logbook and Vessel Monitoring System (VMS)
data \citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more
real-time spatial management has been possible \citep[e.g.][]{Holmes2011}.
Such
information is, however, derived from an inherently biased sampling programme,
targeted fishing, where fishers establish favoured fishing grounds through an
explore-exploit strategy \citep{Bailey2018} where they search for areas with
high catches and then use experience to return to areas where they've
experienced high catch in the past.  \deleted[id=PD]{ Further, fishers
	generally only recorded landings (not catch) on a daily
	basis\todo{\added[id=JJ]{Its not clear what the problem is: landings
			collected on daily basis or landings recorded rather
			than catch}}.  This leads to questions about the
	validity of inference that can be drawn from landings data assigned to
	VMS activity pings.}\todo{\added[id=JJ]{This comes as a surprise: I
		thought this was going to be about
		discards}\added[id=PD]{Agree, have removed this to avoid
		confusion}}\\

@@

Figure \ref{fig:2} shows the consequences of different temporal aggregations of
the data over a ten-year period, with weekly (top), monthly (middle) and yearly
(bottom) catch compositions from across an aggregated 20 x 20 area. By
comparison to the 'real population', the monthly aggregation captures the major
patterns seen in the weekly data, albeit missing more subtle differences. The
yearly data assumes the same proportion of each population caught at any time
of the year due to the data aggregation. This assumption introduces
`aggregation bias' as the data may only be representative of some point (or no
point) in time. The commercial data on a weekly basis shows some of the same
patterns as the 'real population', though the first species (in red) is less
well represented and some weeks are missing catches from the area. The monthly
data shows some consistency between the 'real population' and commercial data
for species 2 - 4, though species 1 remains under-represented. On an annual
basis, interestingly the commercial data under represents the first species (in
red) while the survey over represents species
1. This is likely due to the biases in commercial sampling, with the fisheries
not targeting the areas where species 1 are present, and the biases in the
survey sampling from over representation of
the spatial distribution.

>>>>

\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} appropriate
spatial scales for fisheries closures has been a challenge in the past but
identified as crucial to its success \citep{Costello2010, Dunn2016}. Further,
poorly sited closures have led to ineffectual measures with unintended
consequences. For example, increased benthic impact on previously unexploited
areas was observed from the cod closure in the North Sea with a lack of
observed intended effect in reducing cod exploitation
\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
refined spatiotemporal information has \added[id=PD]{since} become available
through the combination of logbook and Vessel Monitoring System (VMS) data
\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
spatial management has been possible \citep[e.g.][]{Holmes2011}.  Such
information is, however, derived from an inherently biased sampling programme,
targeted fishing, where fishers establish favoured fishing grounds through an
explore-exploit strategy \citep{Bailey2018} where they search for areas with
high catches and then use experience to return to areas where they've
experienced high catch in the past.  \deleted[id=PD]{ Further, fishers
	generally only recorded landings (not catch) on a daily
	basis\todo{\added[id=JJ]{Its not clear what the problem is: landings
			collected on daily basis or landings recorded rather
			than catch}}.  This leads to questions about the
	validity of inference that can be drawn from landings data assigned to
	VMS activity pings.}\todo{\added[id=JJ]{This comes as a surprise: I
		thought this was going to be about
		discards}\added[id=PD]{Agree, have removed this to avoid
		confusion}}\\

@@

Figure \ref{fig:2} shows the consequences of different temporal aggregations of
the data over a ten-year period, with weekly (top), monthly (middle) and yearly
(bottom) catch compositions from across an aggregated 20 x 20 area. By
comparison to the 'real population', the monthly aggregation captures the major
patterns seen in the weekly data, albeit missing more subtle differences. The
yearly data assumes the same proportion of each population caught at any time
of the year due to the data aggregation. This assumption introduces
`aggregation bias' as the data may only be representative of some point (or no
point) in time. The commercial data on a weekly basis shows some of the same
patterns as the 'real population', though the first species (in red) is less
well represented and some weeks are missing catches from the area. The monthly
data shows some consistency between the 'real population' and commercial data
for species 2 - 4, though species 1 remains under-represented. On an annual
basis, interestingly the commercial data under represents the first species (in
red) while the survey over represents species 1. This is likely due to the
biases in commercial sampling, with the fisheries not targeting the areas where
species 1 are present and the survey sampling areas where species 1 is more
abundant than on average.
